Draft1

### 2014-12-12 MiscData/PresentationandPaper/Draft1.Rmd
Re-arranged extra repository data

---
title: "Draft1"
author: "Sam"
date: "December 11, 2014"
output: pdf_document
linestretch: 1.5

---

@@

Additional information on the GEM data used for this research can be seen in the descriptive statistics table included below.

```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis', warning=FALSE}

CD1 <- CD

# Remove uncessesary column
CD1$X <- NULL

# Set Year as factor
CD1[,"Year"] <- as.factor(CD1[,"Year"])

# Rename column
names(CD) <- gsub("PercentPerceived", "PerceivedCapability", names(CD))
names(CD1) <- gsub("PercentPerceived", "PerceivedCapability", names(CD1))

\begin{singlespace}
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis', warning=FALSE}

# Generate descriptive statistics table
stargazer(CD1, type = "latex")
```
\end{singlespace}

@@

@@

# Create a histogram showing the distribution of Way of Teaching
Q <- qplot(WayofTeaching, data = wot, geom = "histogram", binwidth = .05)

Q + theme_bw()
```

In addition to understanding the density of each recorded "Way of Teaching" indicator, it is also helpful to examine the differences in this indicator among OECD countries.  To see this, we have created a figure showing the distribution of the average "Way of Teaching" value over the 2001-2010 period for the OECD countries included in the surveys.  This figure is included below.

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Import GEM data frame
WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")

# Drop unnecessary column 1
WayofTeaching$X <- NULL

# Change data from long to wide format
WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")

# Delete variable name in Year columns
names(WT) <- gsub("WayofTeaching.", "", names(WT))

# Duplicate df for future use
WT2 <- WT

# Generate a new column with mean of all other columns
WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
                                          "2009", "2010")), na.rm = TRUE)

# Drop year columns, leaving only mean column
WT$'2001' <- NULL
WT$'2002' <- NULL
WT$'2003' <- NULL
WT$'2004' <- NULL
WT$'2005' <- NULL
WT$'2006' <- NULL
WT$'2007' <- NULL
WT$'2008' <- NULL
WT$'2009' <- NULL
WT$'2010' <- NULL
WT$'2011' <- NULL
WT$'2012' <- NULL
WT$'2013' <- NULL
WT$row.names <- NULL

# Create 
WT[, 3] <- round(log(WT[, 3]), digits = 2)
```

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
library(googleVis)

# Plot
WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#ece7f2', '#2b8cbe']"
))

@@

image: ![Way of Teaching](https://raw.githubusercontent.com/SamDund/Assign2Education/master/PresentationandPaper/images/WoTmap.png)

@@

-------------------------

Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.  Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.  This relationship can be seen in table 4 below.  This regression output was generated using a simple least square regression model.

@@

############ Running a regression with full df (including omitted variables)
RG1 <- lm(PercentIntention ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)

RG2 <- lm(PercentNascent ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)

RG3 <- lm(PercentOwner ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
```

\begin{singlespace}
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

# Create vector of lables
labels_1 <- c('Way of Teaching', 'Perceived Capabilities', 'Fear of Failure', 'Perceived Good Opportunities', 
             'Fear of Failure x Perceived Good Opportunities')

dlabels_1 <- c('Entrepreneurial Intention', 'Nascent Entrepreneur', 'Entrepreneurship Owner')

# Regression output table with country-specific effects
stargazer::stargazer(RG1, RG2, RG3,
                     title = 'Linear Regression Estimates with Country-specific Effects',
                     covariate.labels = labels_1, dep.var.labels = dlabels_1, digits = 2,
                     font.size =  "scriptsize", type = 'latex', no.space = TRUE)

```
\end{singlespace}

To more clearly demonstrate the relationship between the "Way of Teaching" and our dependent variables, we have omitted the country-specific effects and generated simulations to show demonstrate the outcome of 1000 trials of our regression equation.  Before doing so, however, we ran another set of regressions to determine which equation we would like to examine more closely.  The results can be seen in table 5 below.

# Run three regression equations again (omitting country-specific effects)
RG4 <- lm(PercentIntention ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

RG5 <- lm(PercentNascent ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

RG6 <- lm(PercentOwner ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

\begin{singlespace}
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

# Regression output table with country-specific effects
stargazer::stargazer(RG4, RG5, RG6,
                     title = 'Linear Regression Estimates omitting Country-specific Effects',
                     covariate.labels = labels_1, dep.var.labels = dlabels_1, digits = 2,
                     font.size =  "scriptsize", type = 'latex', no.space = TRUE)

```
\end{singlespace}

Given the positive relationship between the "Way of Teaching" and "Entrepreneurship Owner" we decided to use this equation for our simulations.   In an effort to address data availability issues, we also decided to run a second model including imputed data generated by the R program Amelia to generate an imputed data frame.  This program uses statistical inference to generate imputed data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).  Equation  titled "Imputed" were calculated using this imputed data frame.

To generate the simulations, we decided to use the R package Zelig.  This package allows us to set parameters for an explanatory variable and simulate trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).  We chose to simulate values in our explanatory variable "Way of Teaching" and "Perceived Capabilities" for this analysis.  One important aspect of the Zelig package is that observations with omitted variables will be omitted from the calculation.  For this reason, there is some variation between the coefficients for the Zelig model and the model in the preceeding regression output chart.

Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables." A regression output table and our simulation results are included below.

@@

# Run a least squares regression with Zelig
Z1 <- zelig(PercentOwner ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")

@@

names(CI_omitted) <- gsub("PercentPerceived", "PerceivedCapability", names(CI_omitted))

# Regression equation with imputed values
Z2 <- zelig(PercentOwner ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")

@@

# Set range of PerceivedCapabilities values in simulation (NOT IMPUTED)
x.out1 <- setx(Z1, PerceivedCapability = 9:67)

@@

# Set range of PerceivedCapability values in siumlation (IMPUTED)
x.out2 <- setx(Z2, PerceivedCapability = 9:67)

@@

\begin{singlespace}
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

# Set new vector for dependent variable label
dlabels_2 <- c('Entrepreneurship Owner')

# Regression output table with country-specific effects
stargazer::stargazer(Z1, Z2,
                     title = 'Least Squares Regression for Continuous Dependent Variables',
                     covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
                     font.size =  "small", type = 'latex', no.space = TRUE,
                     notes = "Regression equation 1 is unimputed, regression equation 2 is imputed")
```
\end{singlespace}

@@

@@

# Plot simz1 (unimputed)
plot(simz1, xlab = 'Percent Perceived Capabilities', ylab = 'Percent Entrepreneurship Owner',
     main = "Unimputed (Equation 1)")

# Plot simz2 (imputed)
plot(simz2, xlab = 'Percent Perceived Capabilities', ylab = 'Percent Entrepreneurship Owner',
     main = "Imputed (Equation 2)")

@@

As we can see from the regression output table, using the Amelia program to generate additional data expanded the observations analyzed from 172 to 318, and increased the statistical significance of our explantory variable.  In addition, the positive slope of this equation is consistent with what we expected after our analysis of existing literature on this topic.  In addition, this process reduced the variance in our simulation results, suggesting it improved the accuracy of this model.  Despite this, we have several concerns regarding the reliability of existing GEM data (which will be discussed later in this paper), which makes us question the effectiveness of using this data to generate additional observations.

Perceived opportunities

```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}

# Library required packages
library(googleVis)
library(countrycode)
library(repmis)
library("ggplot2")
library("reshape2")

# Import GEM data frame
PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")

## Add country codes and place new column at beginning of the data frame
# Create a vector of country codes
D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
PerceivedOpportunities$new.col <- D2

# Reorder columns so country code is first
D3 <- PerceivedOpportunities[,c(15,1:14)]

# Rename first column
D4 <- plyr::rename(x = D3, 
                   replace = c("new.col" = "iso2c"))

# Remove X's in D4 year columns
names(D4) <- gsub("X", "", names(D4))

# Set columns as numeric
D4[,"2001"] <- as.numeric(D4[,"2001"])
D4[,"2002"] <- as.numeric(D4[,"2002"])
D4[,"2003"] <- as.numeric(D4[,"2003"])
D4[,"2004"] <- as.numeric(D4[,"2004"])
D4[,"2005"] <- as.numeric(D4[,"2005"])
D4[,"2006"] <- as.numeric(D4[,"2006"])
D4[,"2007"] <- as.numeric(D4[,"2007"])
D4[,"2008"] <- as.numeric(D4[,"2008"])
D4[,"2009"] <- as.numeric(D4[,"2009"])
D4[,"2010"] <- as.numeric(D4[,"2010"])
D4[,"2011"] <- as.numeric(D4[,"2011"])
D4[,"2012"] <- as.numeric(D4[,"2012"])
D4[,"2013"] <- as.numeric(D4[,"2013"])

# Create country vector to subset
myvars2 <- c('US','FR','DE','JP','GB')

# Subset Opp2
Opp2 <- subset(D4, iso2c %in% myvars2)

# Melt Opp2 df
Opp3 <- melt(data = Opp2,
                  id.vars = c("Country", "iso2c"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Edit column names
names(Opp3) <- gsub("value", "PerceivedOpportunities", names(Opp3))
names(Opp3) <- gsub("variable", "Year", names(Opp3))

Opp3$iso2c <- NULL
```

```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

# Create plot
G1 <- ggplot(Opp3,aes(x = Year, y = PerceivedOpportunities, colour = Country, group = Country)) + geom_line()

G1 + ggtitle("Perceived Opportunities Over Time") + theme_bw()
```

>>>>

---
title: "Draft1"
author: "Sam"
date: "December 11, 2014"
output: pdf_document
---

@@

The process of importing, cleaning, and analyzing all of the data used in this project is fully documented and reproducable by referencing our GitHub repository.

@@

..........(Describe why we use the rate of entrepreneurship indicators we chose)

@@

# Create a histogram showing the distribution of Way of Teaching
qplot(WayofTeaching, data = wot, geom = "histogram", binwidth = .10)

@@

@@

Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the  dependent variables we selected as indicators of the entrepreneurship rate.  Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant and has a negative relationship with our explanatory variables.

Overall, however, if we omit country-specific effects, we can demonstrate that the Way of Teaching and the Percent Perceived Good Opportunities are statistically significant in the model indicated below.

We can show the relationship between the dependent and explanatory variables in the four simulations below.  The R package Zelig allows us to set parameters for an explanatory variable and simulate 1000 trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).  We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.  A regression output table has also been included below.

The simulations labeled "Unimputed" were created using only data collected from GEM. This simulation is not possible with missing data, so observations with missing data were omitted.  In an attempt to increase the accuracy of this model, we used the R program Amelia to generate an imputed data frame.  This program uses statistical inference to generate this data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).  Simulations titled "Imputed" were calculated using this imputed data frame.

@@

############ Running a regression with full df (including omitted variables)
RG1 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

RG2 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)

@@

# Run a least squares regression with Zelig
Z1 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")

@@

# Regression equation with imputed values
Z2 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")

@@

# Set range of PercentPerceived values in simulation (NOT IMPUTED)
x.out1 <- setx(Z1, PercentPerceived = 9:67)

@@

# Set range of PercentPerceived values in siumlation (IMPUTED)
x.out2 <- setx(Z2, PercentPerceived = 9:67)

@@

@@

# Plot simz1 (unimputed)
plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
     main = "Unimputed (Equation 1)")

# Plot simz2 (imputed)
plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
     main = "Imputed (Equation 2)")

@@

@@

```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
library(stargazer)

# Create regression output table
labels <- c('Way of Teaching', 'National Level Perceived Capabilities', 'National Level Avg Fear of Failure',
            'National Level Avg Perceived Good Opportunities', 
            'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities',
            '(Intercept)')

dlabels <- c('National Level Average Percent Owning a Business')

```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

stargazer::stargazer(Z1, Z2, covariate.labels = labels, dep.var.labels = dlabels,
                     title = 'Linear Regression Estimates', notes = "Regression equation 1 is unimputed, regression equation 2 is imputed", digits = 2, type = 'html')

```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}

# Run linear regression R1
R1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)

# Run linear regression R2
R2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)

# Run linear regression R3
R3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}

# Library Stargazer for regression output tables
library(stargazer)

# Create regression output table
labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')

dlables <- c('National Level Average Percent Entrepreneurial Intention', 'National Level Nascent Entrepreneural Activity', 'National Level Average Percent Owning a Business')

stargazer::stargazer(R1, R2, R3, covariate.labels = labels, dep.var.labels = dlables,
                     title = 'Linear Regression Estimates', digits = 2)
